---
title: "ClassroomActivities_ModelSelection"
author: "Meagan Sundstrom"
date: "2025-03-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Load packages
```{r, eval=TRUE}
library(tidyverse)
library(glue)
library(MplusAutomation)
library(here)
library(gt)
library(tidyLPA)
library(patchwork)
library(dplyr)
library(ggpubr)
library(effsize)
library(metafor)
```


Read in data 
```{r, eval=TRUE}
combined<-read.csv("LPA_Input.csv")
```

Descriptive statistics
```{r}
combined %>% 
  pivot_longer(CQ:SQ, names_to = "variable") %>% 
  group_by(variable) %>% 
  summarise(mean = mean(value, na.rm = TRUE),
            sd = sd(value, na.rm = TRUE)) 
```

________________________________________________________________________

## `model 1`: Equal variances (fixed) & covariances fixed to zero


```{r, eval=FALSE}
# Before running, create a folder in the project directory called "m1_enum"

lpa_m1  <- lapply(1:6, function(k) { 
  z2 <- if_else(k < 2 , '!' , '')
  z3 <- if_else(k < 3 , '!' , '')
  z4 <- if_else(k < 4 , '!' , '')
  z5 <- if_else(k < 5 , '!' , '')
  z6 <- if_else(k < 6 , '!' , '')
  
lpa_enum  <- mplusObject(
      
  TITLE = glue("M1: Class{k} "), 
  
  VARIABLE = glue(
   "usevar = CQ-SQ;
    classes = c({k}); "),
  
  ANALYSIS = 
   "estimator = mlr; 
    type = mixture;
    starts = 200 50; 
    processors = 10;",
  
  MODEL = glue(
    "!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
     !!!          Syntax replicates default Mplus specification            !!!
     !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
    
     %c#1%
     [CQ-SQ];     !!! means are are freely estimated  (default)
     CQ-SQ(1-8);  !!! variances are fixed to equality (default)
                              !!! covariances are fixed to zero   (default)
{z2} %c#2%
{z2} [CQ-SQ];
{z2} CQ-SQ(1-8);
     
{z3} %c#3%
{z3} [CQ-SQ];
{z3} CQ-SQ(1-8);
     
{z4} %c#4%
{z4} [CQ-SQ];
{z4} CQ-SQ(1-8);

{z5} %c#5%
{z5} [CQ-SQ];
{z5} CQ-SQ(1-8);

{z6} %c#6%
{z6} [CQ-SQ];
{z6} CQ-SQ(1-8);"),
  
  OUTPUT = "sampstat residual tech11 tech14;",
  
  PLOT = 
    "type = plot3; 
     series = CQ-SQ(*);",
  
  usevariables = colnames(combined),
  rdata = combined)

lpa_m1_fit <- mplusModeler(lpa_enum, 
    dataout=glue(here("m1_enum", "c_lpa_m1.dat")),
    modelout=glue(here("m1_enum", "c{k}_lpa_m1.inp")),
    check=TRUE, run = TRUE, hashfilename = FALSE)
})

```

________________________________________________________________________

Model 1: Produce model fit table
```{r}
m1_output <- readModels(here("m1_enum"), quiet = TRUE)

m1_enum <- LatexSummaryTable(m1_output,                               
                keepCols=c("Title","Parameters", "LL", "BIC",         
                           "aBIC", "BLRT_PValue", "T11_VLMR_PValue",
                           "Observations"),    
                sortBy = "Title")                                     

gt(m1_enum)
```

________________________________________________________________________

## `model 2`: Free variances & covariances fixed to zero


```{r, eval=FALSE}
# Before running, create a folder in the project directory called "m2_enum"

lpa_m2  <- lapply(1:6, function(k) { 
  z2 <- if_else(k < 2 , '!' , '')
  z3 <- if_else(k < 3 , '!' , '')
  z4 <- if_else(k < 4 , '!' , '')
  z5 <- if_else(k < 5 , '!' , '')
  z6 <- if_else(k < 6 , '!' , '')
  
lpa_enum  <- mplusObject(
      
  TITLE = glue("M2: Class{k} "), 
  
  VARIABLE = glue(
   "usevar = CQ-SQ;
    classes = c({k}); "),
  
  ANALYSIS = 
   "estimator = mlr; 
    type = mixture;
    starts = 200 50; 
    processors = 10;",
  
  MODEL = glue(
   
   "%c#1%
    [CQ-SQ];   !!! means are are freely estimated
    CQ-SQ;     !!! variances are freely estimated
                           !!! covariances are fixed to zero (default)
{z2} %c#2%
{z2} [CQ-SQ];
{z2} CQ-SQ;
     
{z3} %c#3%
{z3} [CQ-SQ];
{z3} CQ-SQ;
     
{z4} %c#4%
{z4} [CQ-SQ];
{z4} CQ-SQ;

{z5} %c#5%
{z5} [CQ-SQ];
{z5} CQ-SQ;

{z6} %c#6%
{z6} [CQ-SQ];
{z6} CQ-SQ;

"),
  
  OUTPUT = "sampstat residual tech11 tech14;",
  
  PLOT = 
    "type = plot3; 
     series = CQ-SQ(*);",
  
  usevariables = colnames(combined),
  rdata = combined)

lpa_m2_fit <- mplusModeler(lpa_enum, 
    dataout=glue(here("m2_enum", "c_lpa_m2.dat")),
    modelout=glue(here("m2_enum", "c{k}_lpa_m2.inp")) ,
    check=TRUE, run = TRUE, hashfilename = FALSE)
})

```

________________________________________________________________________

Model 2: Produce model fit table
```{r}
m2_output <- readModels(here("m2_enum"), quiet = TRUE)

m2_enum <- LatexSummaryTable(m2_output,                               
                keepCols=c("Title","Parameters", "LL", "BIC",         
                           "aBIC", "BLRT_PValue", "T11_VLMR_PValue",
                           "Observations"),     
                sortBy = "Title")                                     

gt(m2_enum)
```

________________________________________________________________________

## `model 3`: Equal (fixed) variances & free covariances 

```{r, eval=FALSE}
# Before running, create a folder in the project directory called "m3_enum"

lpa_m3  <- lapply(1:6, function(k) { 
  z2 <- if_else(k < 2 , '!' , '')
  z3 <- if_else(k < 3 , '!' , '')
  z4 <- if_else(k < 4 , '!' , '')
  z5 <- if_else(k < 5 , '!' , '')
  z6 <- if_else(k < 6 , '!' , '')
  
lpa_enum  <- mplusObject(
      
  TITLE = glue("M3: Class{k} "), 
  
  VARIABLE = glue(
   "usevar = CQ-SQ;
    classes = c({k}); "),
  
  ANALYSIS = 
   "estimator = mlr; 
    type = mixture;
    starts = 200 50; 
    processors = 10;",
  
  MODEL = glue(
    
   "%c#1%
    [CQ-SQ];          !!! means are freely estimated
    CQ-SQ(1-8);       !!! variances are fixed to equality
    CG with WG;       !!! covariances are freely estimated
    CG with OG;
    CG with SQ;
    CG with Lec;
    CG with PQ;
    CG with CQ;
    CG with MG;
    WG with OG;
    WG with SQ;
    WG with Lec;
    WG with PQ;
    WG with CQ;
    WG with MG;
    OG with SQ;
    OG with Lec;
    OG with PQ;
    OG with CQ;
    OG with MG;
    SQ with Lec;
    SQ with PQ;
    SQ with CQ;
    SQ with MG;
    Lec with PQ;
    Lec with CQ;
    Lec with MG;
    PQ with CQ;
    PQ with MG;
    CQ with MG;
   
{z2} %c#2%
{z2} [CQ-SQ];
{z2} CQ-SQ(1-8);
{z2} CG with WG;       
{z2} CG with OG;
{z2} CG with SQ;
{z2} CG with Lec;
{z2} CG with PQ;
{z2} CG with CQ;
{z2} CG with MG;
{z2} WG with OG;
{z2} WG with SQ;
{z2} WG with Lec;
{z2} WG with PQ;
{z2} WG with CQ;
{z2} WG with MG;
{z2} OG with SQ;
{z2} OG with Lec;
{z2} OG with PQ;
{z2} OG with CQ;
{z2} OG with MG;
{z2} SQ with Lec;
{z2} SQ with PQ;
{z2} SQ with CQ;
{z2} SQ with MG;
{z2} Lec with PQ;
{z2} Lec with CQ;
{z2} Lec with MG;
{z2} PQ with CQ;
{z2} PQ with MG;
{z2} CQ with MG;
     
{z3} %c#3%
{z3} [CQ-SQ];
{z3} CQ-SQ(1-8);
{z3} CG with WG;       
{z3} CG with OG;
{z3} CG with SQ;
{z3} CG with Lec;
{z3} CG with PQ;
{z3} CG with CQ;
{z3} CG with MG;
{z3} WG with OG;
{z3} WG with SQ;
{z3} WG with Lec;
{z3} WG with PQ;
{z3} WG with CQ;
{z3} WG with MG;
{z3} OG with SQ;
{z3} OG with Lec;
{z3} OG with PQ;
{z3} OG with CQ;
{z3} OG with MG;
{z3} SQ with Lec;
{z3} SQ with PQ;
{z3} SQ with CQ;
{z3} SQ with MG;
{z3} Lec with PQ;
{z3} Lec with CQ;
{z3} Lec with MG;
{z3} PQ with CQ;
{z3} PQ with MG;
{z3} CQ with MG;

{z4} %c#3%
{z4} [CQ-SQ];
{z4} CQ-SQ(1-8);
{z4} CG with WG;       
{z4} CG with OG;
{z4} CG with SQ;
{z4} CG with Lec;
{z4} CG with PQ;
{z4} CG with CQ;
{z4} CG with MG;
{z4} WG with OG;
{z4} WG with SQ;
{z4} WG with Lec;
{z4} WG with PQ;
{z4} WG with CQ;
{z4} WG with MG;
{z4} OG with SQ;
{z4} OG with Lec;
{z4} OG with PQ;
{z4} OG with CQ;
{z4} OG with MG;
{z4} SQ with Lec;
{z4} SQ with PQ;
{z4} SQ with CQ;
{z4} SQ with MG;
{z4} Lec with PQ;
{z4} Lec with CQ;
{z4} Lec with MG;
{z4} PQ with CQ;
{z4} PQ with MG;
{z4} CQ with MG;

{z5} %c#3%
{z5} [CQ-SQ];
{z5} CQ-SQ(1-8);
{z5} CG with WG;       
{z5} CG with OG;
{z5} CG with SQ;
{z5} CG with Lec;
{z5} CG with PQ;
{z5} CG with CQ;
{z5} CG with MG;
{z5} WG with OG;
{z5} WG with SQ;
{z5} WG with Lec;
{z5} WG with PQ;
{z5} WG with CQ;
{z5} WG with MG;
{z5} OG with SQ;
{z5} OG with Lec;
{z5} OG with PQ;
{z5} OG with CQ;
{z5} OG with MG;
{z5} SQ with Lec;
{z5} SQ with PQ;
{z5} SQ with CQ;
{z5} SQ with MG;
{z5} Lec with PQ;
{z5} Lec with CQ;
{z5} Lec with MG;
{z5} PQ with CQ;
{z5} PQ with MG;
{z5} CQ with MG;

{z6} %c#3%
{z6} [CQ-SQ];
{z6} CQ-SQ(1-8);
{z6} CG with WG;       
{z6} CG with OG;
{z6} CG with SQ;
{z6} CG with Lec;
{z6} CG with PQ;
{z6} CG with CQ;
{z6} CG with MG;
{z6} WG with OG;
{z6} WG with SQ;
{z6} WG with Lec;
{z6} WG with PQ;
{z6} WG with CQ;
{z6} WG with MG;
{z6} OG with SQ;
{z6} OG with Lec;
{z6} OG with PQ;
{z6} OG with CQ;
{z6} OG with MG;
{z6} SQ with Lec;
{z6} SQ with PQ;
{z6} SQ with CQ;
{z6} SQ with MG;
{z6} Lec with PQ;
{z6} Lec with CQ;
{z6} Lec with MG;
{z6} PQ with CQ;
{z6} PQ with MG;
{z6} CQ with MG;"),
  
  OUTPUT = "sampstat residual tech11 tech14;",
  
  PLOT = 
    "type = plot3; 
     series = CQ-SQ(*);",
  
  usevariables = colnames(combined),
  rdata = combined)

lpa_m3_fit <- mplusModeler(lpa_enum, 
    dataout=glue(here("m3_enum", "c_lpa_m3.dat")),
    modelout=glue(here("m3_enum", "c{k}_lpa_m3.inp")),
    check=TRUE, run = TRUE, hashfilename = FALSE)
})

```

________________________________________________________________________

Model 3: Produce model fit table
```{r}
m3_output <- readModels(here("m3_enum"), quiet = TRUE)

m3_enum <- LatexSummaryTable(m3_output,                                   
                keepCols=c("Title","Parameters", "LL", "BIC",             
                           "aBIC", "BLRT_PValue", "T11_VLMR_PValue",
                           "Observations"),    
                sortBy = "Title")                                         

gt(m3_enum)
```

________________________________________________________________________
## `model 4`: Free variances & free covariances 

```{r, eval=FALSE}
# Before running, create a folder in the project directory called "m4_enum"

lpa_m4  <- lapply(1:6, function(k) { 
  z2 <- if_else(k < 2 , '!' , '')
  z3 <- if_else(k < 3 , '!' , '')
  z4 <- if_else(k < 4 , '!' , '')
  z5 <- if_else(k < 5 , '!' , '')
  z6 <- if_else(k < 6 , '!' , '')
  
lpa_enum  <- mplusObject(
      
  TITLE = glue("M4: Class{k} "), 
  
  VARIABLE = glue(
   "usevar = CQ-SQ;
    classes = c({k}); "),
  
  ANALYSIS = 
   "estimator = mlr; 
    type = mixture;
    starts = 200 50; 
    processors = 10;",
  
  MODEL = glue(
    
   "%c#1%
    [CQ-SQ];          !!! means are freely estimated
    CQ-SQ;       !!! variances are fixed to equality
    CG with WG;       !!! covariances are freely estimated
    CG with OG;
    CG with SQ;
    CG with Lec;
    CG with PQ;
    CG with CQ;
    CG with MG;
    WG with OG;
    WG with SQ;
    WG with Lec;
    WG with PQ;
    WG with CQ;
    WG with MG;
    OG with SQ;
    OG with Lec;
    OG with PQ;
    OG with CQ;
    OG with MG;
    SQ with Lec;
    SQ with PQ;
    SQ with CQ;
    SQ with MG;
    Lec with PQ;
    Lec with CQ;
    Lec with MG;
    PQ with CQ;
    PQ with MG;
    CQ with MG;
   
{z2} %c#2%
{z2} [CQ-SQ];
{z2} CQ-SQ;
{z2} CG with WG;       
{z2} CG with OG;
{z2} CG with SQ;
{z2} CG with Lec;
{z2} CG with PQ;
{z2} CG with CQ;
{z2} CG with MG;
{z2} WG with OG;
{z2} WG with SQ;
{z2} WG with Lec;
{z2} WG with PQ;
{z2} WG with CQ;
{z2} WG with MG;
{z2} OG with SQ;
{z2} OG with Lec;
{z2} OG with PQ;
{z2} OG with CQ;
{z2} OG with MG;
{z2} SQ with Lec;
{z2} SQ with PQ;
{z2} SQ with CQ;
{z2} SQ with MG;
{z2} Lec with PQ;
{z2} Lec with CQ;
{z2} Lec with MG;
{z2} PQ with CQ;
{z2} PQ with MG;
{z2} CQ with MG;

{z3} %c#3%
{z3} [CQ-SQ];
{z3} CQ-SQ;
{z3} CG with WG;       
{z3} CG with OG;
{z3} CG with SQ;
{z3} CG with Lec;
{z3} CG with PQ;
{z3} CG with CQ;
{z3} CG with MG;
{z3} WG with OG;
{z3} WG with SQ;
{z3} WG with Lec;
{z3} WG with PQ;
{z3} WG with CQ;
{z3} WG with MG;
{z3} OG with SQ;
{z3} OG with Lec;
{z3} OG with PQ;
{z3} OG with CQ;
{z3} OG with MG;
{z3} SQ with Lec;
{z3} SQ with PQ;
{z3} SQ with CQ;
{z3} SQ with MG;
{z3} Lec with PQ;
{z3} Lec with CQ;
{z3} Lec with MG;
{z3} PQ with CQ;
{z3} PQ with MG;
{z3} CQ with MG;

{z4} %c#3%
{z4} [CQ-SQ];
{z4} CQ-SQ;
{z4} CG with WG;       
{z4} CG with OG;
{z4} CG with SQ;
{z4} CG with Lec;
{z4} CG with PQ;
{z4} CG with CQ;
{z4} CG with MG;
{z4} WG with OG;
{z4} WG with SQ;
{z4} WG with Lec;
{z4} WG with PQ;
{z4} WG with CQ;
{z4} WG with MG;
{z4} OG with SQ;
{z4} OG with Lec;
{z4} OG with PQ;
{z4} OG with CQ;
{z4} OG with MG;
{z4} SQ with Lec;
{z4} SQ with PQ;
{z4} SQ with CQ;
{z4} SQ with MG;
{z4} Lec with PQ;
{z4} Lec with CQ;
{z4} Lec with MG;
{z4} PQ with CQ;
{z4} PQ with MG;
{z4} CQ with MG;

{z5} %c#3%
{z5} [CQ-SQ];
{z5} CQ-SQ;
{z5} CG with WG;       
{z5} CG with OG;
{z5} CG with SQ;
{z5} CG with Lec;
{z5} CG with PQ;
{z5} CG with CQ;
{z5} CG with MG;
{z5} WG with OG;
{z5} WG with SQ;
{z5} WG with Lec;
{z5} WG with PQ;
{z5} WG with CQ;
{z5} WG with MG;
{z5} OG with SQ;
{z5} OG with Lec;
{z5} OG with PQ;
{z5} OG with CQ;
{z5} OG with MG;
{z5} SQ with Lec;
{z5} SQ with PQ;
{z5} SQ with CQ;
{z5} SQ with MG;
{z5} Lec with PQ;
{z5} Lec with CQ;
{z5} Lec with MG;
{z5} PQ with CQ;
{z5} PQ with MG;
{z5} CQ with MG;

{z6} %c#3%
{z6} [CQ-SQ];
{z6} CQ-SQ;
{z6} CG with WG;       
{z6} CG with OG;
{z6} CG with SQ;
{z6} CG with Lec;
{z6} CG with PQ;
{z6} CG with CQ;
{z6} CG with MG;
{z6} WG with OG;
{z6} WG with SQ;
{z6} WG with Lec;
{z6} WG with PQ;
{z6} WG with CQ;
{z6} WG with MG;
{z6} OG with SQ;
{z6} OG with Lec;
{z6} OG with PQ;
{z6} OG with CQ;
{z6} OG with MG;
{z6} SQ with Lec;
{z6} SQ with PQ;
{z6} SQ with CQ;
{z6} SQ with MG;
{z6} Lec with PQ;
{z6} Lec with CQ;
{z6} Lec with MG;
{z6} PQ with CQ;
{z6} PQ with MG;
{z6} CQ with MG;"),
  
  OUTPUT = "sampstat residual tech11 tech14;",
  
  PLOT = 
    "type = plot3; 
     series = CQ-SQ(*);",
  
  usevariables = colnames(combined),
  rdata = combined)

lpa_m4_fit <- mplusModeler(lpa_enum, 
    dataout=glue(here("m4_enum", "c_lpa_m4.dat")),
    modelout=glue(here("m4_enum", "c{k}_lpa_m4.inp")),
    check=TRUE, run = TRUE, hashfilename = FALSE)
})

```

________________________________________________________________________

Model 4: Produce model fit table

```{r}
m4_output <- readModels(here("m4_enum"), quiet = TRUE)

m4_enum <- LatexSummaryTable(m4_output,                                 
                keepCols=c("Title","Parameters", "LL", "BIC",           
                           "aBIC", "BLRT_PValue", "T11_VLMR_PValue",    
                           "Observations"),                             
                sortBy = "Title")                                       

gt(m4_enum)
```

________________________________________________________________________

## Final table of model fit (`all models`) 

```{r, eval=TRUE}

allFit <- rbind(m1_enum,m2_enum,m3_enum,m4_enum)
                   
allFit1 <- allFit %>% 
  mutate(aBIC = -2*LL+Parameters*log((Observations+2)/24)) %>% 
  mutate(CAIC = -2*LL+Parameters*(log(Observations)+1)) %>% 
  mutate(AWE = -2*LL+2*Parameters*(log(Observations)+1.5)) %>%
  mutate(SIC = -.5*BIC) %>% 
  mutate(expSIC = exp(SIC - max(SIC))) %>% 
  mutate(BF = exp(SIC-lead(SIC))) %>% 
  mutate(cmPk = expSIC/sum(expSIC)) %>% 
  dplyr::select(1:5,9:10,6:7,13,14) 

```

Format the model fit table 
```{r, eval=TRUE}

allFit1 %>% 
  mutate(Title = str_remove_all(Title, "M...")) %>% 
  gt() %>%
  tab_header(
    title = md("**Model Fit Summary Table**"), subtitle = md("&nbsp;")) %>% 
  cols_label(
    Title = "Classes",
    Parameters = md("Par"),
    LL = md("*LL*"),
    T11_VLMR_PValue = "VLMR",
    BLRT_PValue = "BLRT",
    BF = md("BF"),
    cmPk = md("*cmPk*")) %>%
  tab_footnote(
    footnote = md(
    "*Note.* Par = Parameters; *LL* = model log likelihood;
      BIC = Bayesian information criterion;
      aBIC = sample size adjusted BIC; CAIC = consistent Akaike information criterion;
      AWE = approximate weight of evidence criterion;
      BLRT = bootstrapped likelihood ratio test p-value;
      VLMR = Vuong-Lo-Mendell-Rubin adjusted likelihood ratio test p-value;
      *cmPk* = approximate correct model probability."), 
    locations = cells_title()) %>% 
  tab_options(column_labels.font.weight = "bold") %>% 
  fmt_number(10,decimals = 2,
             drop_trailing_zeros=TRUE,
             suffixing = TRUE) %>% 
  fmt_number(c(3:9,11), 
             decimals = 2) %>% 
  sub_missing(1:11,
              missing_text = "--") %>% 
  fmt(c(8:9,11),
    fns = function(x) 
    ifelse(x<0.001, "<.001",
           scales::number(x, accuracy = 0.01))) %>%
  fmt(10, fns = function(x) 
    ifelse(x>100, ">100",
           scales::number(x, accuracy = .1))) %>%
  tab_row_group(
    label = "Model-1",
    rows = 1:6) %>%
  tab_row_group(
    label = "Model-2",
    rows = 7:12) %>%
  tab_row_group(
    label = "Model-3",
    rows = 13:18) %>%
  tab_row_group(
    label = "Model-4",
    rows = 19:24) %>%
  row_group_order(
      groups = c("Model-1","Model-2","Model-3","Model-4")) %>% 
tab_style(style = list(cell_text(weight = "bold")),
  locations = list(
  cells_body(columns = BIC, row = BIC == min(BIC[c(1:6)])),
  cells_body(columns = BIC, row = BIC == min(BIC[c(7:12)])),
  cells_body(columns = BIC, row = BIC == min(BIC[c(13:18)])),
  cells_body(columns = BIC, row = BIC == min(BIC[c(19:24)])),
  cells_body(columns = aBIC, row = aBIC == min(aBIC[c(1:6)])),
  cells_body(columns = aBIC, row = aBIC == min(aBIC[c(7:12)])),
  cells_body(columns = aBIC, row = aBIC == min(aBIC[c(13:18)])),
  cells_body(columns = aBIC, row = aBIC == min(aBIC[c(19:24)])),
  cells_body(columns = CAIC, row = CAIC == min(CAIC[c(1:6)])),
  cells_body(columns = CAIC, row = CAIC == min(CAIC[c(7:12)])),
  cells_body(columns = CAIC, row = CAIC == min(CAIC[c(13:18)])),
  cells_body(columns = CAIC, row = CAIC == min(CAIC[c(19:24)])),
  cells_body(columns = AWE, row = AWE == min(AWE[c(1:6)])),
  cells_body(columns = AWE, row = AWE == min(AWE[c(7:12)])),
  cells_body(columns = AWE, row = AWE == min(AWE[c(13:18)])),
  cells_body(columns = AWE, row = AWE == min(AWE[c(19:24)])),
  cells_body(columns = cmPk, row =  cmPk > .001),
  cells_body(columns = BF, row =  BF > 10),
  cells_body(columns =  T11_VLMR_PValue,
  row =ifelse(T11_VLMR_PValue < .001 & lead(T11_VLMR_PValue) > .001, T11_VLMR_PValue < .001, NA)),
  cells_body(columns =  BLRT_PValue,
  row =ifelse(BLRT_PValue < .001 & lead(BLRT_PValue) > .001, BLRT_PValue < .001, NA))))

```


________________________________________________________________________

**Plot information criteria:**

```{r}
allFit1 %>%
  dplyr::select(1, 4:7) %>%
  rowid_to_column() %>%
  pivot_longer(`BIC`:`AWE`,
               names_to = "Index",
               values_to = "ic_value") %>% 
  separate(Title, c('Model', 'Class'), sep = ": Class")  %>% 
  mutate(Class = as.numeric(Class)) %>%
  mutate(Index = factor(Index,
                        levels = c ("AWE", "CAIC", "BIC", "aBIC"))) %>%
  ggplot(aes(x = Class, y = ic_value,
    color = Index, shape = Index, group = Index, lty = Index)) +
  facet_wrap(~Model,nrow=1) +
  geom_point(size = 2.0) + geom_line(size = .8) +
  scale_x_continuous(breaks = 1:nrow(allFit)) +
  theme_minimal() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),axis.ticks.y = element_line(color = "black", size = 0.5),axis.ticks.x=element_line(color = "black", size = 0.5))+
  labs(x = "Number of Profiles", y = "Information Criteria Value") +
  theme(text = element_text(size = 10),
    legend.text = element_text(size=10),
    legend.key.width = unit(3, "line"), legend.title = element_blank(),
    legend.position = "top")+
  theme(panel.border = element_rect(color = "black", fill = NA, size = 0.5))+
  theme(strip.background = element_rect(colour='black', size=0.5),strip.text=element_text(size=10,color='black'))


```


```{r}
# Assign each observation to their most probable profile for the model-1, 4-profile solution
m_step1  <- mplusObject(
  
  TITLE = glue("M1: Class4 "), 
  
  VARIABLE = glue(
   "usevar = CQ-SQ;
    classes = c(4); "),
  
  ANALYSIS = 
   "estimator = mlr; 
    type = mixture;
    starts = 200 50; 
    processors = 10;
    optseed = 565819;",
  
  SAVEDATA = 
   "!!! This saved dataset will contain class probabilities and modal assignment columns !!!
    File=3step_savedata.dat;
    Save=cprob;
    Missflag= 999;",
  
  usevariables = colnames(combined),
  rdata = combined)

m_step1_fit <- mplusModeler(m_step1,
                 dataout="step1_3step.dat",
                 modelout="step1_3step.inp" ,
                 check=TRUE, run = TRUE, hashfilename = FALSE)

logit_cprobs <- as.data.frame(m_step1_fit[["results"]]
                                         [["class_counts"]]
                                         [["logitProbs.mostLikely"]])

savedata <- as.data.frame(m_step1_fit[["results"]]
                                     [["savedata"]])

colnames(savedata)[colnames(savedata)=="C"] <- "Profile"

combined_assignment<-cbind(combined,savedata$Profile)

combined_assignment <- combined_assignment %>% mutate(Profile=ifelse(combined_assignment$`savedata$Profile`==3,4,ifelse(combined_assignment$`savedata$Profile`==4,3,combined_assignment$`savedata$Profile`)))

combined_assignment <- combined_assignment %>% dplyr::select(-12)

```